Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2017-10-25 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
Add results plots (overlap and nrejects)

---
title: "Comparison of FDR methods on GWAS with SummarizedBenchmark"
author: "Keegan Korthauer"
date: "10/19/2017"
output: html_document
---

@@

for 2,458,133 SNPs.

@@

### experimenting on a subset of the full dataset for now
bmi <- bmi[1:50000,]
```

@@

```{r, GWAS1-metrics}
# rename assay to qvalue
names(assays(sb)) <- names(rowData(sb)) <- names(sb@performanceMetrics) <- "qvalue"
sb <- addDefaultMetrics(sb)
sb

head(assay(sb))
colData(sb)
sb@performanceMetrics[[1]]

# estimate perf metrics
sb <- estimatePerformanceMetrics(sb, alpha=seq(0.01, 0.10, 0.01), addColData=TRUE)
colData( sb )
```

@@

## to add here - standardized plotting functions from SummarizedBenchmarks -
## to discuss at meeting 10/19

# alpha versus nrejects

# upset plot

@@

```{r, GWAS1-cleanup}
rm(bmi)
rm(bd)
rm(sb)
```

>>>>

---
title: "Comparison of FDR methods on GWAS with SummarizedBenchmark"
author: "Keegan Korthauer"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

@@

for `r nrow(bmi)` SNPs.

@@

### experimenting on a subset of the full dataset for now
bmi <- bmi[1:500000,]
```

@@

```{r, GWAS1-metrics}
# rename assay to qvalue
assayNames(sb) <- "qvalue"
names(rowData(sb)) <- names(sb@performanceMetrics) <- "qvalue"
sb <- addDefaultMetrics(sb)

head(assay(sb))
head(colData(sb))
sb@performanceMetrics[[1]]

# estimate perf metrics and store in tidy format for plotting
pf <- estimatePerformanceMetrics(sb, alpha=seq(0.01, 0.10, 0.01), tidy=TRUE)
```

@@

# plot adjusted p-values by independent covariate
plotsim_single(data.frame(assay(sb)), bmi, strat = "ind_covariate")

# alpha versus nrejects
plotsim_average(pf, met="rejections", merge_ihw = TRUE) +
  ggtitle("Number of rejections for BMI dataset")

# alpha versus nrejects (excluding "unadjusted")
plotsim_average(pf, met="rejections", filter_set = "unadjusted", merge_ihw = TRUE) +
  ggtitle("Number of rejections for BMI dataset")

# upset plot
plotMethodsOverlap(sb, alpha=0.1, nsets=ncol(sb))

# upset plot excluding "unadjusted"
plotMethodsOverlap(sb[,-1], alpha=0.1, nsets=ncol(sb)-1)
```

@@

```{r, GWAS1-cleanup}
rm(bmi)
rm(bd)
rm(sb)
rm(pf)
```
